Exploring the Motives and Driving Forces Behind Modifications to APIs From a Software Evolution Perspective

### 2015-04-30 thesis/acm/paper.tex
added note to acknowl

@@

@@

\section{Acknowledgments}

>>>>

\section{Discussion}

@@

Look up the papers from the conference (especially regarding the discussion/conclusion)
discussion = revisiting research questions (and maybe structuring around industry/academia)
conclusion = summary part, main final points and future work

Stuff for the conclusion:
Have a more structured feedback loop (include users) this can be future work too
Include more scientific theories

@@

\section{Acknowledgments}
We would like to thank Axis and that project at GU.
